---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# GRAFit (R package)

<!-- badges: start -->
<!-- badges: end -->

**GRAFit** is an modular automatic pipeline for galaxy structural decomposition originally designed for the Hubble Space Telescope (HST) imaging data, the Advanced Camera for Surveys (ACS) in particular. However, it can be used for any standard astronomical imaging data. 
<!-- At it's core GRAFit uses ProFit galaxy fitting package. -->

## Installation

### Install R

Get **R** for OSX (Mac), Linux and Windows from: [https://cloud.r-project.org](https://cloud.r-project.org)

### Install ProFit

**GRAFit** uses **ProFit**, a Bayesian galaxy profile fitting tool.

Get **ProFit** with:

``` {r eval = FALSE}
install.packages('devtools')
library(devtools)
install_github("ICRAR/ProFit")
library(ProFit)
```

See [ProFit](https://github.com/ICRAR/ProFit) if you faced any issues with installing ProFit or it's dependencies.


### Install ProFound

**GRAFit** uses **ProFound** for photometry and source extraction and generating segmentation map.

Get **ProFound** with:

``` {r eval = FALSE}
devtools::install_github("asgr/ProFound")
library(ProFound)
```

This should work properly, and the dependencies should be installed automatically.

See [ProFound](https://github.com/asgr/ProFound) if you faced any issues with installing **ProFound**.


### Install Tiny Tim
**GRAFit** uses **Tiny Tim** for generating HST Point Spread Function (PSF).

Get **Tiny Tim** from [here](https://www.stsci.edu/hst/instrumentation/focus-and-pointing/focus/tiny-tim-hst-psf-modeling)


### Install GRAFit
<!-- You can install the released version of GRAFit from [CRAN](https://CRAN.R-project.org) with:-->
<!-- ``` r -->
<!-- install.packages("GRAFit") -->
<!-- ``` -->

You can install **GRAFit** from [GitHub](https://github.com/hoseinhashemi/GRAFit) with:

``` {r eval = FALSE}
devtools::install_github("hoseinhashemi/GRAFit")
library(GRAFit)
```

### Dependencies

Most of the required dependencies should be installed by this stage. 
In case any of the dependencies are failed to install, you can install them with.

```{r eval = FALSE}
install.packages(c('fftw', 'R2Cuba', 'RColorBrewer', 'EBImage', 'LaplacesDemon', 'imager', 'magicaxis', 'FITSio', 'data.table'))
```

The segmentation map required for **GRAFit** is generated by **ProFound** using **EBImage** package. If this package was not installed by this stage install it with:

```{r eval = FALSE}
install.packages("BiocManager")
BiocManager::install("EBImage")
```


## Example

**GRAFit** is originally designed for a large number of galaxies distributed between one or more imaging frames, although there is no restriction for fitting one galaxy in a single cutout.
In principle, you need to interact with only one **GRAFit** function; `GRAFitMaster`. This function calls all other modules and dependencies during fitting process.

You should provide:
* a working directory where the outputs will be saved.

* a directory where your imaging data is stored.

* If any, a directory where you have stored your pre-generated Point Spread Function (PSF) for each object. Otherwise, you may leave a PSF in your `wrk_dir` or alternatively GRAFit will generate a HST PSF using **Tiny Tim**. In the later you will beed to provide the PSF specifications required by **Tiny Tim**.

For a simple run, I provide a folder including a COSMOS HST/ACS frames together with its associated PSF and an input catalogue.
Download the whole folder from [here](https://www.dropbox.com/sh/pb8xri702tz03ka/AAB7hwuy89jhyqRHUwuMrBK0a?dl=0) and put it where you wish in you local directory, suppose in your Desktop.

Then run the code below for a basic example of **GRAFit** fitting. 


```{r eval = FALSE}

inCat = read.csv('~/Desktop/GRAFit_test_Run/Input.csv')

GRAFitMaster(wrk_dir = "~/Desktop/GRAFit_test_Run/",
             data_dir = "~/Desktop/GRAFit_test_Run/",
             threadMode = 0,
             ncores = 1,
             nComp= 2,
             optimMode = 'optim',
             object_list = inCat)
```

* Note that `object_list` should include at least the RA and DEC.

This run uses a relatively simple `optim` optimizer to save you some time. More robust optimization that **GRAFit* provides is MCMC for which you need to specify optimMode = 'MCMC'. See `GRAFitMaster` documentation for more details and options. 

This run will genrate a folder named with the galaxy ID (or RA/DEC if ID is not provided in inCat) containing all outputs associated with this galaxy such as figures of initial and optimized model, 1D profiles etc. In addition it will generate a master catalogue (MasterCat.csv) in you `wrk_dir` directory including all fitting parameters as well as a ProCat.csv including the results of photometric measurements by ProFound. Another directory could be also generated containing work spaces for which you need to specify `keep_wrk_space = TRUE`. 


## Contributor(s)
Hosein Hashemizadeh

## License
L-GPL3

